\documentclass[12pt]{constitution}
\usepackage{mathpazo}
\usepackage{datetime}
\newdate{reviseddate}{11}{11}{2015}
\usepackage{hyperref}
\usepackage{cleveref}
\renewcommand{\sectionautorefname}{\S}
\begin{document}
\title{Constitution}
\author{WMTU}
\date{\displaydate{reviseddate}}
\maketitle
\setcounter{tocdepth}{1}
\tableofcontents
\newpage

We, the students of Michigan Technological University, recognizing the need for a radio station to cater to the musical tastes of the student body and provide an educational service to the community, do hereby ordain this constitution for the operation of a student radio station, so that this need might be served.


\article{Name}


The name of the organization shall be WMTU 91.9 FM, hereafter referred to as either `WMTU' or `the Station'.


\article{Purpose}


The purpose of WMTU shall be:
\begin{enumerate}
\item To provide Michigan Technological University and the surrounding community with alternative high quality radio programming.
\item To provide the students of Michigan Technological University with an opportunity to participate in the operation of a radio station.
\item To organize and facilitate events which might provide the student body and local community with concerts, shows, fundraisers, and other opportunities of social significance.
\end{enumerate}


\article{Membership}


\section{General Staff}
\begin{enumerate}
\item Members of the General Staff of WMTU must be students or employees at Michigan Technological University.
\item Members of General staff are considered either Active or Inactive.
\begin{enumerate}
\item The rules of Active Staff Membership are as follows:
\begin{enumerate}
\item A person is eligible to be appointed to Active General Staff after he or she has attended 3 General Staff meetings or has been present through the entirety of one senior staff election.
\item Active Staff members shall have one vote at General Staff meetings.
\item Any active member who fails to attend three consecutive General Staff meetings without giving prior notice to the secretary (WMTU Const. IV.1 \cref{attendance}) or appointed attendance keeper shall be considered Inactive Staff.
\end{enumerate}
\item The rules of Inactive Staff Membership are as follows:
\begin{enumerate}
\item An Inactive Staff member retains all rights of, and must abide by all rules which apply to active general staff members except the ability to vote in general staff meetings.
\item Attendance of three consecutive General Staff meetings by an inactive staff member is required to return to Active Staff, and active membership is re­established at the beginning of the third consecutive attended meeting.
\end{enumerate}
\end{enumerate}
\end{enumerate}


\section{Senior Staff}
\begin{enumerate}
\item The Senior Staff of WMTU shall consist of a General Manager, a Secretary, plus eight Department Heads, whose titles shall be as follows:
\begin{itemize}
\item Business Manager
\item Programming Director
\item Public Relations Liaison
\item Broadcast Supervisor
\item Production Supervisor
\item Chief Audio Engineer
\item Chief Computer Engineer
\item Event Coordinator
\end{itemize}
\item The responsibilities of the Senior Staff shall be as follows:
\begin{enumerate}
\item The Senior Staff shall serve as the Executive Committee of WMTU. Their duties are described in Article I of the Bylaws.
\item Members of the Senior Staff must be full-­time students or an employee at Michigan Technological University and students must have cumulative grade point averages of at least 2.25 ​at the time of election. Only one employee shall be on senior staff at any given time. Only a student may be elected General Manager.
\item Each member of the Senior Staff shall have one vote at General Staff meetings and one vote at Senior Staff meetings, with the exception of the General Manager, who shall only vote in the event of a tie.
\item Senior Staff members shall be elected each year.
\item As vacancies occur within Senior Staff, the General Manager shall appoint a member of General Staff to the vacant position. In the event that the General Manager position becomes vacant, Senior Staff shall nominate a member of General Staff to complete the term of the General Manager. A majority vote of General Staff is required to approve the appointment of any member of Senior Staff.
\item An individual may spend a total of no more than two years in any given Senior Staff position.
\item The Senior Staff shall be considered a part of the General Staff.
\end{enumerate}
\end{enumerate}


\section{Enlisted Staff}
\begin{enumerate}
\item The Enlisted Staff of WMTU shall consist of an assistant to each department head, along with specialty roles assigned by the Senior Staff including, but not limited to, the following:
\begin{itemize}
\item Music Director(s)
\item Webmaster
\item Talk Show Engineer(s)
\item Productions Liaison
\item Social Marketing Head
\item Event Department Liaisons
\end{itemize}
\item The responsibilities of the Enlisted Staff are as follows:
\begin{enumerate}
\item The Enlisted Staff shall serve as delegates of their respective department heads. Their duties are outlined in Article I of the Bylaws, but may be given specific directives from their respective department heads.
\item An individual must be considered an Active General Staff member to be appointed as an Enlisted Staff member.
\item The Enlisted Staff shall be appointed each semester, and as necessary.
\item The Enlisted Staff shall be considered a part of the General Staff.
\end{enumerate}
\item In the event an Enlisted Staff member cannot or does not fulfill their duty as their role dictates, their dismissal is subject to the discretion of their respective department head.
\end{enumerate}


\section{​Air Staff}
\begin{enumerate}
\item The Air Staff of WMTU shall be made up of its show hosts.
\item Members of the Air Staff must be students or employees of Michigan Technological University or have written permission by the General Manager, Business Manager, and Broadcast Supervisor.
\item Members of the Air Staff shall not have the power to vote at either General or Senior Staff meetings.
\item Air Staff members shall be appointed or reappointed at the start of each academic semester by the Broadcast Supervisor.
\end{enumerate}


\section{​Advisors for WMTU}
\begin{enumerate}
\item Advisors for WMTU shall be chosen by the General Staff. The Advisors shall not have the power to vote at either General or Senior Staff meetings.
\item The WMTU advisors shall be required to attend 50\% of all Senior Staff meetings. Senior Staff shall be responsible for enforcing this policy.
\end{enumerate}


\section{​Equal Opportunity Policy}
In compliance with Michigan Technological University's Board of Control Equal Opportunity Policy effective February 24, 2011, WMTU shall not discriminate on the basis of race, religion, color, national origin, age, sex, sexual orientation, gender identity, height, weight, genetic information, or marital status. In addition, the organization is committed to the policy of not discriminating against disabled individuals and veterans.


\article{Meetings}


\section{​General Staff Meetings}
\begin{enumerate}
\item General Staff meetings shall be called by the General Manager at least once per week during the academic year, excluding term breaks, and at other times deemed necessary.
\item\label{attendance} Unless excused beforehand by the General Manager or his or her designate, attendance of General Staff meetings is mandatory for all Senior Staff members, Enlisted Staff members, and General Staff members within the organization. In the event attendance to a General Staff meeting by a staff member is not possible, prior notice must be given to the Secretary (or attendance record keeper as designated by the General Manager).
\item The purpose of General Staff meetings shall be to review budget expenditures, approve expenditures outside of the budget, approve amendments to the Constitution and Bylaws, elect Senior Staff members, appoint General Staff members, approve General Staff appointments, take action concerning the removal or reinstatement of Staff members, and make other decisions concerning the smooth operation of the Station.
\item A majority of Active General Staff members must be present to constitute a quorum at a General Staff meeting.
\item The General Manager shall only vote at General Staff meetings in the event of a tie.
\item Unless otherwise stated, a majority vote of all General Staff members present shall be required to pass a motion.
\end{enumerate}


\section{Senior Staff Meetings}
\begin{enumerate}
\item Senior Staff meetings shall be called by the General Manager at least once per week during the academic year, excluding breaks, and at other times deemed necessary.
\item Senior Staff meeting absences shall be handled as follows:
\begin{enumerate}
\item Unless excused beforehand by the General Manager or his/her designate, or there is a known academic conflict, attendance is mandatory for all Senior Staff members and Enlisted Staff members at Senior Staff meetings.
\item In the event a member of Senior Staff is absent from a Senior Staff meeting, a representative must be appointed from his/her department to provide updates and take notes.
\item Repeat offences may result in the review, and possible suspension, of a Senior Staff member's position.
\end{enumerate}
\item The purpose of Senior Staff meetings shall be to:
\begin{itemize}
\item Maintain communications and coordinate efforts amongst departments.
\item Provide recommendations to General Staff.
\item Approve the Station Budget.
\item Approve expenditures within the limits of the Budget.
\item Discuss and draft amendments to the constitution and bylaws, and
\item Engage in all activities that are required to facilitate the operation of the station.
\end{itemize}
\item A two-­thirds majority of the Senior Staff members or their designates must be present to constitute a quorum.
\item Unless otherwise stated, a majority vote of the Senior Staff members or their designates present shall be required to pass a motion.
\end{enumerate}


\section{Department Meetings}
\begin{enumerate}
\item Department meetings shall be called by the Department Heads at least once per two weeks during the academic year, and at other times deemed necessary.
\item Unless excused beforehand by the respective Department Head or his/her designate, attendance is mandatory for all staff members of each department at their respective department meetings.
\end{enumerate}


\article{Finances}


\section{​Derivation of Funds}
WMTU shall derive its financial support through:
\begin{itemize}
\item Funding from the Student Activities Fee (SAF);
\item Underwriting;
\item Sponsoring fundraising activities;
\item Other legal means.
\end{itemize}


\section{​Asset Holding}
Station funds shall be held by Michigan Technological University in a student organization account.


\section{​Station Budget}
Within the first four weeks of each spring semester, an annual Station Budget shall be drafted by the Business Manager and the business department with input from Senior Staff.
\begin{enumerate}
\item The Budget shall outline spending for the next academic year.
\item The preliminary Budget shall be presented to Senior Staff and Senior Staff Appointees during the sixth week of the Spring Semester. Senior Staff and Senior Staff Appointees shall review and suggest revisions to the Budget.
\item The final Budget must be approved by the Senior Staff prior to the eighth week of the spring semester.
\item The final Budget shall be submitted to Student Activities for approval.
\end{enumerate}


\section{​Allocation of Assets}
\begin{enumerate}
\item Senior Staff may allocate funds within the limits of the Budget.
\item The General Staff shall be apprised of any expense approved by Senior Staff at the following General Staff meeting. Any item over \$100 must be approved with a majority vote from General Staff before being purchased.
\item The Senior Staff may allocate up to \$100 outside of any item's budget, so long as the expense stays within the limits of the rollover or maintenance amount stated in the Budget.
\item Leftover funds from purchases in the budget shall be available for allocation to additional purchases, and become rollover if unused during the current fiscal year.
\end{enumerate}


\section{​Purchases}
\begin{enumerate}
\item Purchases under \$5000 shall be made using the purchasing card assigned to WMTU by MTU purchasing department. Purchases made with the Purchasing card shall be made in accordance with University regulations.
\item Purchases over \$5000 shall be made using a Michigan Tech Purchase order.
\end{enumerate}


\article{Ratification and Amendments}


\section{​Approval of Constitution and Bylaws}
This Constitution and Bylaws shall be declared adopted upon approval by a two-thirds majority vote of the General Staff members at a General Staff meeting and the Office of Student Activities.


\section{​Amendments to Constitution or Bylaws}
\begin{enumerate}
\item Amendments to the Constitution and Bylaws may be presented in writing at any regularly scheduled General Staff meeting and be voted on no sooner than the next General Staff meeting, provided that at least one week is allowed to elapse between the two meetings.
\item A two-­thirds majority vote of the General Staff members present shall be required for the passage of an amendment.
\item Any amendments to the Constitution and Bylaws shall become effective upon receiving approval from the Office of Student Activities.
\end{enumerate}

\end{document}